---
title: "Spotify Analysis"
author: "Cam Smithers"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
library(tidyverse)
library(ggplot2)
library(ggiraph)
library(htmltools)
library(hrbrthemes)
library(readxl)
library(viridis)
library(stringr)
```

# Cam's Spotify Streaming History

## Data Cleaning

1.  Loading in data
2.  Selecting variable I want to keep
3.  Renaming variables
4.  Dropping rows with missing values
5.  Changing the date column from character to date
6.  Creating a column for the specific year

```{r}
streaming_data <- read_csv("/Users/camsmithers/Desktop/Data/combined_data.csv")

streaming_data <- streaming_data %>%
    select(ts, ms_played, master_metadata_track_name,
           master_metadata_album_artist_name,
           master_metadata_album_album_name,
           spotify_track_uri, reason_start, reason_end,
           shuffle, skipped) %>%
    rename(
        "play_timestamp"="ts", "millisec_played"="ms_played",
        "song"="master_metadata_track_name",
        "album"="master_metadata_album_album_name",
        "artist"="master_metadata_album_artist_name") %>%
    drop_na() %>%
    mutate(play_timestamp = as.Date(play_timestamp)) %>%
    mutate(play_year = as.factor(year(play_timestamp)))
```

## Personal Favorites

Artists/Albums/Songs

1.  Selecting needed vars

2.  Filtering for favorite artists/albums/songs

3.  Using `unique()` to only have one observation

4.  Creating a column to specify it's a favorite of mine

```{r}
favorite_artists <-streaming_data %>%
    select(artist) %>%
    filter(
        artist == "H.E.R." | artist == "Kehlani" | artist == "Drake" |
        artist == "Ariana Grande" | artist == "UMI" | artist == "Jenevieve" |
        artist == "Alina Baraz" | artist == "Lil Tecca" |
        artist == "Muni Long" | artist == "J. Cole" | artist == "NIKI" |
        artist == "Mac Ayres") %>%
    unique() %>%
    mutate(favorite_artist = "Yes")

favorite_albums <- streaming_data %>%
    select(album, artist) %>%
    filter(
        (album == "H.E.R." & artist == "H.E.R.") |
            (album == "Back of My Mind" & artist == "H.E.R.") |
            (album == "Forest in the City" & artist == "UMI") |
            (album == "Her Loss" & artist == "Drake") |
            (album == "Championships" & artist == "Meek Mill") |
            (album == "SweetSexySavage" & artist == "Kehlani") |
            (album == "blue water road" & artist == "Kehlani") |
            (album == "Public Displays Of Affection: The Album" & 
                 artist == "Muni Long") |
            (album == "Sweetener" & artist == "Ariana Grande") |
            (album == "It Was Divine" & artist == "Alina Baraz") |
            (album == "The Color of You" & artist == "Alina Baraz") |
            (album == "thank u, next" & artist == "Ariana Grande") |
            (album == "Rendezvous - EP" & artist == "Jenevieve") |
            (album == "Harry's House" & artist == "Harry Styles") |
            (album == "NEVER ENOUGH" & artist == "Daniel Caesar") |
            (album == "Fetty Wap" & artist == "Fetty Wap")) %>%
    unique() %>%
    mutate(favorite_album = "Yes")

favorite_songs <- streaming_data %>%
    select(song, artist) %>%
    filter(
        (artist == "H.E.R." & (song == "Changes" | song == "Gone Away" | 
             song == "Rather Be" | song == "Jungle" | song == "My Own")) |
            (artist == "Meek Mill" & 
                 song == "Dangerous (feat. Jeremih and PnB Rock)") | 
            (artist == "UMI" & (song == "moonlit room" |
                 song == "Love Affair")) |
            (artist == "Eric Bellinger" & song == "Goat 2.0 (feat. Wale)") |
            (artist == "Drake" & song == "Spin Bout U") |
            (artist == "Metro Boomin" & 
                 song == "Trance (with Travis Scott & Young Thug)") |
            (artist == "21 Savage" & song == "prove it") |
            (artist == "Kehlani" & (song == "As I Am" | song == "melt" | 
                 song == "After Hours")) |
            (artist == "Lil Tecca" & song == "MONEY ON ME") |
            (artist == "Lil Baby" & song == "Go Hard") | 
            (artist == "Jenevieve" & 
                 (song == "Love Quotes" | song == "Nxwhere")) |
            (artist == "Bryson Tiller" & song == "Years Go By") |
            (artist == "Carly Rae Jepsen" & song == "Run Away With Me") |
            (artist == "Harry Styles" & song == "Satellite")) %>%
    unique() %>%
    mutate(favorite_song = "Yes")
```

## Cumulative Counts (by Year and Overall)

Yearly Cumulative Counts

1.  Arrange by date
2.  Group by...
    -   Song, Artist, and Year Played
    -   Artist and Year Played
    -   Album, Artist, and Year Played
3.  Running total of the number of times the artist/song/album was played
4.  Remove the groupings

All Time Cumulative Counts

1.  Arrange by date
2.  Group by...
    -   Song and Artist
    -   Artist
    -   Album and Artist
3.  Running total of the number of times the artist/song/album was played
4.  Remove the groupings

```{r}
#Total Count by Year for Songs, Artists, Albums
streaming_data_2 <- streaming_data %>%
    #Yearly Running Total
    
    ##Song Count
    arrange(play_timestamp) %>%
    group_by(song, artist, play_year) %>%
    mutate(yearly_song_cumsum = row_number(song)) %>%
    ungroup() %>%
    ##Artist Count
    arrange(play_timestamp) %>%
    group_by(artist, play_year) %>%
    mutate(yearly_artist_cumsum = row_number(artist)) %>%
    ungroup() %>%
    ##Album Count
    arrange(play_timestamp) %>%
    group_by(album, artist, play_year) %>%
    mutate(yearly_album_cumsum = row_number(album)) %>%
    ungroup() %>%
    
    #All Time Running Total
    
    ##Song Count
    arrange(play_timestamp) %>%
    group_by(song, artist) %>%
    mutate(alltime_song_cumsum = row_number(song)) %>%
    ungroup() %>%
    ##Artist Count
    arrange(play_timestamp) %>%
    group_by(artist) %>%
    mutate(alltime_artist_cumsum = row_number(artist)) %>%
    ungroup() %>%
    ##Artist Count
    arrange(play_timestamp) %>%
    group_by(album, artist) %>%
    mutate(alltime_album_cumsum = row_number(album)) %>%
    ungroup()
```

## All Time Songs/Artists/Albums Plays

1.  Group by...
    -   Song and Artist
    -   Artist
    -   Album and Artist
2.  Count the number of observations
3.  Sort the values (high to low)

```{r}
alltime_songs <- streaming_data_2 %>%
    group_by(song, artist) %>%
    summarize(alltime_song_count = n(), .groups = "drop") %>%
    arrange(desc(alltime_song_count))

alltime_artists <- streaming_data_2 %>%
    group_by(artist) %>%
    summarize(alltime_artist_count = n(), .groups = "drop") %>%
    arrange(desc(alltime_artist_count))

alltime_albums <- streaming_data_2 %>%
    group_by(album, artist) %>%
    summarize(alltime_album_count = n(), .groups = "drop") %>%
    arrange(desc(alltime_album_count))
```

## Yearly Top 10 Songs/Artists/Albums (by number of plays)

Yearly Top 10 Songs/Artists/Albums

1.  Group by...
2.  Get the maximum cumulative sum
3.  Sort the observations by the year played, then by the number of plays
4.  Group by the year played
5.  Select the top ten values for each year
6.  Column to specify if a song/artist/album was top ten in a respective year

Unique Songs/Artists/Albums

1.  Using `distinct()` to remove duplicates that were top ten in multiple years

```{r}
yearly_top10_songs <- streaming_data_2 %>%
    group_by(play_year, song, artist) %>%
    summarize(yearly_top10_songs_count = max(yearly_song_cumsum),
              .groups = "drop") %>%
    arrange(play_year, desc(yearly_top10_songs_count)) %>%
    group_by(play_year) %>%
    slice_head(n = 10) %>%
    mutate(year_x_top10_song = "Top 10 Song")

yearly_top10_artists <- streaming_data_2 %>%
    group_by(play_year, artist) %>%
    summarize(yearly_top10_artists_count = max(yearly_artist_cumsum),
              .groups = "drop")%>%
    arrange(play_year, desc(yearly_top10_artists_count)) %>%
    group_by(play_year) %>%
    slice_head(n = 10) %>%
    mutate(year_x_top10_artist = "Top 10 Artist")

yearly_top10_albums <- streaming_data_2 %>%
    group_by(play_year, album, artist) %>%
    summarize(yearly_top10_albums_count = max(yearly_album_cumsum),
              .groups = "drop") %>%
    arrange(play_year, desc(yearly_top10_albums_count)) %>%
    group_by(play_year) %>%
    slice_head(n = 10) %>%
    mutate(year_x_top10_album = "Top 10 Album")

top_unique_songs <- yearly_top10_songs %>%
    distinct(song, artist)

top_unique_artists <- yearly_top10_artists %>%
    distinct(artist)

top_unique_albums <- yearly_top10_albums %>%
    distinct(album, artist)
```

## Joining Data

Using left join to bring summary data frames into the main data frame

```{r}
spotify_data <- streaming_data_2 %>%
    left_join(alltime_songs, by = c("song", "artist")) %>%
    left_join(alltime_artists, by = "artist") %>%
    left_join(alltime_albums, by = c("album", "artist")) %>%
    left_join(yearly_top10_songs, by = c("play_year", "song", "artist")) %>%
    left_join(yearly_top10_artists, by = c("play_year", "artist")) %>%
    left_join(yearly_top10_albums, by = c("play_year", "album", "artist")) %>%
    left_join(favorite_songs, by = c("artist", "song")) %>%
    left_join(favorite_artists, by = "artist") %>%
    left_join(favorite_albums, by = c("artist", "album"))
```

## Data Cleaning 2

Column to identify if a song/artist/album is its respective unique list

```{r}
spotify_data_2 <- spotify_data %>%
    mutate(
        ever_top10_song = if_else(
            (artist %in% top_unique_songs$artist) & 
                (song %in% top_unique_songs$song), "Yes", NA),
        ever_top10_artist = if_else(
            artist %in% top_unique_artists$artist, "Yes", NA),
        ever_top10_album = if_else(
            (artist %in% top_unique_albums$artist) & 
                (album %in% top_unique_albums$album), "Yes", NA))
```

## Plotting Data

All Time Song/Artist/Album Plot Data: Joining main data to respective plot data.

```{r eval=FALSE, include=FALSE}
song_plot_data <- spotify_data_2 %>%
    filter(!is.na(ever_top10_song))

artist_plot_data <- spotify_data_2 %>%
    filter(!is.na(ever_top10_artist)) %>%
    mutate(artist = gsub("'", "", artist))

album_plot_data <- spotify_data_2 %>%
    filter(!is.na(ever_top10_album))
```

```{r}
alltime_songs_plot_data <- alltime_songs %>%
    left_join(spotify_data_2, by = c("song", "artist", "alltime_song_count"))

alltime_albums_plot_data <- alltime_albums %>%
    left_join(spotify_data_2, by = c("album", "artist", "alltime_album_count"))

alltime_artists_plot_data <- alltime_artists %>%
    left_join(spotify_data_2, by = c("artist", "alltime_artist_count"))
```

------------------------------------------------------------------------

# Listening Analysis

## All Songs/Artists/Albums

### 10 Most Played Songs/Artists/Albums of All Time

```{r}
#Most Listened to Songs of All Time
top10_songs_oat_bar <- ggplot(alltime_songs %>%
                              slice_head(n = 10),
                          aes(x = alltime_song_count, y = song,
                              fill = artist)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    geom_text(aes(label = alltime_song_count), 
              hjust = 1.05,
              size = 4) +
    theme_bw() +
    labs(
        title = "10 Most Played Songs (2019-2025)",
        fill = "Song",
        y = "Name of Song",
        x = "Play Count"
    )
top10_songs_oat_bar

#Most Listened to Artists of All Time
top10_artists_oat_bar <- ggplot(alltime_artists %>%
                                slice_head(n = 10),
                            aes(x = alltime_artist_count, y = artist,
                                fill = artist)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    geom_text(aes(label = alltime_artist_count), 
              hjust = 1.05,
              size = 4) +
    theme_bw() +
    labs(
        title = "10 Most Played Artists (2019-2025)",
        fill = "Artist",
        y = "Name of Artists",
        x = "Play Count"
    )
top10_artists_oat_bar

#Most Listened to Albums of All Time
top10_albums_oat_bar <- ggplot(alltime_albums %>%
                               slice_head(n = 10),
                           aes(x = alltime_album_count, y = album,
                               fill = artist)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    geom_text(aes(label = alltime_album_count), 
              hjust = 1.05,
              size = 4) +
    theme_bw() +
    labs(
        title = "10 Most Played Albums (2019-2025)",
        fill = "Artist",
        y = "Name of Album",
        x = "Play Count (a song played on album)"
    )
top10_albums_oat_bar
```

### 10 Most Played Songs by Year

```{r}
#Most Listened to Songs of All Time
music_years <- unique(spotify_data_2$play_year)

for (music_year in music_years) {
    yearly_top10_songs_bar <- ggplot(yearly_top10_songs %>%
                                     filter(play_year == music_year),
                          aes(x = yearly_top10_songs_count, y = song,
                              fill = artist)) +
        geom_bar(stat = "identity", position = "dodge", color = "black") +
        geom_text(aes(label = yearly_top10_songs_count), 
              hjust = 1.05,
              size = 4) +
        theme_bw() +
        labs(
        title = paste("10 Most Played Songs in", music_year),
        fill = "Artist",
        y = "Name of Song",
        x = "Play Count"
        )
    print(yearly_top10_songs_bar)
}
```

### 10 Most Played Artists by Year

```{r}
for (music_year in music_years) {
    yearly_top10_artists_bar <- ggplot(yearly_top10_artists %>%
                                     filter(play_year == music_year),
                          aes(x = yearly_top10_artists_count, y = artist,
                              fill = artist)) +
        geom_bar(stat = "identity", position = "dodge", color = "black") +
        geom_text(aes(label = yearly_top10_artists_count), 
              hjust = 1.05,
              size = 4) +
        theme_bw() +
        labs(
        title = paste("10 Most Played Artists in", music_year),
        fill = "Artist",
        y = "Name of Artist",
        x = "Play Count"
        )
    print(yearly_top10_artists_bar)
}
```

### 10 Most Played Albums by Year

```{r}
for (music_year in music_years) {
    yearly_top10_albums_bar <- ggplot(yearly_top10_albums %>%
                                     filter(play_year == music_year),
                          aes(x = yearly_top10_albums_count, y = album,
                              fill = artist)) +
        geom_bar(stat = "identity", position = "dodge", color = "black") +
        geom_text(aes(label = yearly_top10_albums_count), 
              hjust = 1.05,
              size = 4) +
        theme_bw() +
        labs(
        title = paste("10 Most Played Albums in", music_year),
        fill = "Artist",
        y = "Name of Album",
        x = "Play Count"
        )
    print(yearly_top10_albums_bar)
    }
```

## Favorite Songs/Artists/Albums Statistics

### Play Count of Favorite Songs/Artists/Albums

```{r}
fav_songs_oat_bar <- ggplot(alltime_songs_plot_data %>%
                            filter(favorite_song == "Yes") %>%
                            mutate(
                                song = fct_reorder(song, alltime_song_count)
                                ) %>%
                            distinct(song, artist, alltime_song_count),
                        aes(x = alltime_song_count, y = song, fill = artist)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    theme_bw() +
    labs(
        title = "Favorite Songs Play Count",
        fill = "Song",
        y = "Name of Song",
        x = "Play Count"
    )
fav_songs_oat_bar

fav_albums_oat_bar <- ggplot(alltime_albums_plot_data %>%
                            filter(favorite_album == "Yes") %>%
                            mutate(
                                album = fct_reorder(album, alltime_album_count)
                                ) %>%
                            distinct(album, artist, alltime_album_count),
                        aes(x = alltime_album_count, y = album, fill = artist)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    theme_bw() +
    labs(
        title = "Favorite Albums Play Count",
        fill = "Artist",
        y = "Name of Album",
        x = "Play Count (played a song on the album)"
    )
fav_albums_oat_bar

fav_artists_oat_bar <- ggplot(alltime_artists_plot_data %>%
                              filter(favorite_artist == "Yes") %>%
                              mutate(
                                  artist = fct_reorder(artist, 
                                                       alltime_artist_count)
                                  ) %>%
                              distinct(artist, alltime_artist_count),
                          aes(x = alltime_artist_count, y = artist,
                              fill = artist)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    scale_x_continuous(
        breaks = seq(0, max(alltime_artists_plot_data$alltime_artist_count),
                     by = 5000)) +
    theme_bw() +
    labs(
        title = "Favorite Artists Play Count",
        fill = "Artist",
        y = "Name of Artist",
        x = "Play Count"
    )
fav_artists_oat_bar
```

### 10 Most Played Songs for Favorite Artist

```{r}
for (music_artist in favorite_artists$artist) {
    artist_top10_songs_bar <- ggplot(alltime_songs %>%
                                         mutate(song = str_wrap(song, width = 20)) %>%
                                         filter(artist == music_artist) %>%
                                         slice_head(n = 10),
                                     aes(x = alltime_song_count, y = song,
                              fill = song)) +
        geom_bar(stat = "identity", position = "dodge", color = "black") +
        geom_text(aes(label = alltime_song_count), 
              hjust = 1.05,
              size = 4) +
        theme_bw() +
        labs(
            title = paste(music_artist, "Top 10 Played Songs"),
            y = "Song",
            x = "Play Count",
            fill = "Song"
        )
    print(artist_top10_songs_bar)
}
```

### Top 5 Songs from Favorite Albums

```{r}
for (music_album in favorite_albums$album) {
    album_loop_data <- streaming_data_2 %>%
        filter(album == music_album) %>%
        group_by(song) %>%
        summarize(song_album_count = n(), .groups = "drop") %>%
        arrange(desc(song_album_count)) %>%
        slice_head(n = 5)
    
    top5_album_songs <- ggplot(album_loop_data %>%
                               mutate(song = str_wrap(song, width = 20)),
                               aes(x = song_album_count,
                                   y = song,
                                   fill = song)) +
        geom_bar(stat = "identity", position = "dodge", color = "black") +
        theme_bw() +
        labs(
            title = paste("Top 5 Played Song on", music_album),
            y = "Song",
            x = "Play Count",
            fill = "Song"
        )
    print(top5_album_songs)
}
```

## 10 Most Played Songs/Artists/Albums (of All Time) Over Time

```{r}
#Most Listened to Songs of All Time
alltime_songs_2 <- alltime_songs %>%
    arrange(desc(alltime_song_count)) %>%
    slice_head(n = 10)


top10_songs_oat_bytime <- ggplot(alltime_songs_plot_data %>%
                                     filter(
                                         song %in% alltime_songs_2$song & 
                                             artist %in% alltime_songs_2$artist & 
                                             alltime_song_count %in%
                                             alltime_songs_2$alltime_song_count),
                          aes(x = play_timestamp,
                              y = alltime_song_cumsum,
                              color = song)) +
    geom_path() + 
    theme_bw() +
    labs(
        title = "10 Most Played Songs (2019-2025)",
        color = "Song",
        x = "Time",
        y = "Play Count"
    )
top10_songs_oat_bytime 

#Most Listened to Artists of All Time
alltime_artists_2 <- alltime_artists %>%
    arrange(desc(alltime_artist_count)) %>%
    slice_head(n = 10)

top10_artists_oat_bytime <- ggplot(alltime_artists_plot_data %>%
                                       filter(
                                           artist %in% alltime_artists_2$artist & 
                                               alltime_artist_count %in%
                                               alltime_artists_2$alltime_artist_count),
                            aes(x = play_timestamp,
                                y = alltime_artist_cumsum,
                                color = artist)) +
    geom_path() +
    theme_bw() +
    labs(
        title = "10 Most Played Artists (2019-2025)",
        color = "Artist",
        x = "Time",
        y = "Play Count"
    )
top10_artists_oat_bytime 

#Most Listened to Albums of All Time
alltime_albums_2 <- alltime_albums %>%
    arrange(desc(alltime_album_count)) %>%
    slice_head(n = 10)

top10_albums_oat_bytime  <- ggplot(alltime_albums_plot_data %>%
                                       filter(
                                           album %in% alltime_albums_2$album &
                                               artist %in% alltime_albums_2$artist &
                                               alltime_album_count %in%
                                               alltime_albums_2$alltime_album_count),
                           aes(x = play_timestamp, 
                               y = alltime_album_cumsum, color = album)) +
    geom_path() +
    theme_bw() +
    labs(
        title = "10 Most Played Albums (2019-2025)",
        color = "Album",
        x = "Time",
        y = "Play Count (a song played on album)"
    )
top10_albums_oat_bytime 
```

### 10 Most Played Songs (in Each Year) Over the Year

```{r}
for (music_year in music_years) {
    yearly_top10_songs_bytime<- ggplot(alltime_songs_plot_data %>%
                                         filter(play_year == music_year &
                                                    year_x_top10_song == "Top 10 Song"),
                                     aes(x = play_timestamp,
                                         y = yearly_song_cumsum,
                                         color = song)) +
        geom_path() +
        scale_color_viridis_d(option = "turbo") +
        theme_bw() +
        labs(
            title = paste("10 Most Played Songs in", music_year),
            color = "Song",
            x = "Time",
            y = "Play Count"
            )
    print(yearly_top10_songs_bytime) 
}
```

### 10 Most Played Artists (in Each Year) Over the Year

```{r}
for (music_year in music_years) {
    yearly_top10_artists_bytime<- ggplot(alltime_artists_plot_data %>%
                                             filter(
                                                 play_year == music_year &
                                                        year_x_top10_artist == "Top 10 Artist"),
                                     aes(x = play_timestamp,
                                         y = yearly_artist_cumsum,
                                         color = artist)) +
        geom_path() +
        scale_color_viridis_d(option = "turbo") +
        theme_bw() +
        labs(
            title = paste("10 Most Played Artists in", music_year),
            color = "Artist",
            x = "Time",
            y = "Play Count"
            )
    print(yearly_top10_artists_bytime) 
    }
```

### 10 Most Played Albums (in Each Year) Over the Year

```{r}
for (music_year in music_years) {
    yearly_top10_albums_bytime<- ggplot(alltime_albums_plot_data %>%
                                            filter(
                                                play_year == music_year &
                                                    year_x_top10_album == "Top 10 Album"),
                                     aes(x = play_timestamp,
                                         y = yearly_album_cumsum,
                                         color = album)) +
        geom_path() + 
        scale_color_viridis_d(option = "turbo") +
        theme_bw() +
        labs(
            title = paste("10 Most Played Albums in", music_year),
            color = "Album",
            x = "Time",
            y = "Play Count (played a song on the album)"
            )
    print(yearly_top10_albums_bytime) 
    }
```

## Significant Dates

Music has been something I've always loved, most days I listen to music for hours upon hours. When I'm feeling certain emotions or I'm going through something significant, I tend to turn to music that aligns with those emotions.

```{r}
significant_dates <- c("2020-10-23", "2021-06-26", "2021-12-25", "2022-02-14",
                       "2022-05-11", "2022-07-10", "2022-09-07", "2022-11-12",
                       "2022-12-24", "2024-11-05", "2025-02-14", "2025-03-11")
significant_dates <- as.Date(significant_dates)

daily_songs <- streaming_data_2 %>%
    group_by(play_timestamp, song, artist) %>%
    summarize(daily_song_count = n(), .groups = "drop") %>%
    arrange(play_timestamp, desc(daily_song_count)) %>%
    group_by(play_timestamp) %>%
    slice_head(n = 5)

for (sig_date in significant_dates) {
    sig_date_plot <- ggplot(daily_songs %>%
               filter(play_timestamp == sig_date),
           aes(x = daily_song_count, y = song, fill = artist)) +
        geom_bar(stat = "identity", position = "dodge", color = "black") +
        theme_bw() +
        labs(
            title = paste("Top 5 Songs On", as.Date(sig_date),
                          ifelse(
                              as.Date(sig_date) %in% 
                                  as.Date(c("2021-06-26","2021-12-25",
                                            "2022-07-10", "2022-02-14",
                                            "2022-05-11","2025-02-14",
                                            "2025-03-11")),
                              "(Favorite Days)", "(Worst Days)")),
            y = "Song Name",
            x = "Play Count",
            fill = "Artist"
        )
    print(sig_date_plot)
    }
```
